---
format: 
  revealjs:
    css: '../configuracao/painel.unidade.css'
    slide-number: c/t
    embed-resources: true
    auto-slide: 10000
    transition: slide
    transition-speed: fast
    background-transition: fade
    loop: true
    menu: false
params:
  Id: '3VCv'
---

```{r setup, include=FALSE}
endereco <- '../dados/Indicadores.rds'
selecao <- c(params$Id, 'Limite', 'Nome', 'Descrição')
indicadores <- readr::read_rds(endereco)
dados <- dplyr::filter(indicadores, Id %in% selecao)
unidade <- dados$Unidade[4]
criar.tabela <- function(tabela) {
  valor <- tabela$Valor |> 
    stringr::str_remove('%') |>
    stringr::str_replace(',', '.') |> 
    as.numeric()

  limite <- as.numeric(tabela$Limite)

  cor.fonte <- ifelse(valor > limite, 'blue', 'red')

  tabela <- tabela |> dplyr::select(-Limite) |> tidyr::pivot_longer(cols = everything(), values_to = 'Valores') |> dplyr::select(-name)

  kableExtra::kable(
    tabela,
    align = 'c',
    escape = FALSE,
    row.names = FALSE,
    col.names = NULL
  ) |>
    kableExtra::kable_styling(font_size = '1.5em',
                              full_width = TRUE,
                              position = 'center') |>
    kableExtra::row_spec(0:nrow(tabela), extra_css = 'border-bottom: none;') |>
    kableExtra::row_spec(1, bold = T, font_size = '1.5em') |>
    kableExtra::row_spec(2, bold = T, font_size = '2em', color = cor.fonte) |>
    kableExtra::row_spec(3, bold = T, font_size = '.5em')
}
```

# Painel da Unidade <br> `r unidade` {background-image="imagens/0.painel.unidade.png" background-opacity=".2"}
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Meta1'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Meta3'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'TCL'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Parados30'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Parados100'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Audiencias'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'TMT'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r unidade`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'IAD'

tabela <- dplyr::tibble(
  Nome = dplyr::pull(dados[2, ], indicador),
  Valor = dplyr::pull(dados[4, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Limite = dplyr::pull(dados[1, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
