---
format: 
  revealjs:
    css: 'configuracao/painel.unidade.css'
    slide-number: c/t
    embed-resources: true
    auto-slide: 10000
    transition: slide
    transition-speed: fast
    background-transition: fade
    loop: true
    menu: false
params:
  Id: 'GEL'
---

```{r setup, include=FALSE}
endereco <- 'dados/indicadores.rds'
indicadores <- readr::read_rds(endereco) |> purrr::pluck(1)

selecao <-
  c(params$Id,
    'Limite',
    'Nome',
    'Descrição',
    'Polaridade',
    'Medida')
dados <- dplyr::filter(indicadores, Id %in% selecao)

vara <- indicadores$Unidade[6]

criar.tabela <- function(tabela) {
  valor <- tabela$Valor |>
    stringr::str_remove('%') |>
    stringr::str_replace(',', '.') |>
    as.numeric()
  
  limite <- as.numeric(tabela$Limite)
  
  cor.fonte <- ifelse(ifelse(tabela$Polaridade == 'maior melhor', valor > limite, valor < limite), 'blue', 'red')
  
  tabela <-
    tabela |>
    dplyr::select(Nome, Valor, Descrição) |>
    tidyr::pivot_longer(cols = everything(), values_to = 'Valores') |>
    dplyr::select(-name)
  
  kableExtra::kable(
    tabela,
    align = 'c',
    escape = FALSE,
    row.names = FALSE,
    col.names = NULL
  ) |>
    kableExtra::kable_styling(font_size = '1.5em',
                              full_width = TRUE,
                              position = 'center') |>
    kableExtra::row_spec(0:nrow(tabela), extra_css = 'border-bottom: none;') |>
    kableExtra::row_spec(1, bold = T, font_size = '1.5em') |>
    kableExtra::row_spec(2,
                         bold = T,
                         font_size = '2em',
                         color = cor.fonte) |>
    kableExtra::row_spec(3, bold = T, font_size = '.5em')
}
```

# Painel da Unidade <br> `r vara` {background-image="imagens/0.painel.unidade.png" background-opacity=".2"}
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r vara`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Meta1'

tabela <- dplyr::tibble(
  Limite = dplyr::pull(dados[1, ], indicador),
  Nome = dplyr::pull(dados[2, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Polaridade = dplyr::pull(dados[4, ], indicador),
  Medida = dplyr::pull(dados[5, ], indicador),
  Valor = dplyr::pull(dados[6, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r vara`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Meta2'

tabela <- dplyr::tibble(
  Limite = dplyr::pull(dados[1, ], indicador),
  Nome = dplyr::pull(dados[2, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Polaridade = dplyr::pull(dados[4, ], indicador),
  Medida = dplyr::pull(dados[5, ], indicador),
  Valor = dplyr::pull(dados[6, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r vara`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'TCL'

tabela <- dplyr::tibble(
  Limite = dplyr::pull(dados[1, ], indicador),
  Nome = dplyr::pull(dados[2, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Polaridade = dplyr::pull(dados[4, ], indicador),
  Medida = dplyr::pull(dados[5, ], indicador),
  Valor = dplyr::pull(dados[6, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r vara`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Parados30'

tabela <- dplyr::tibble(
  Limite = dplyr::pull(dados[1, ], indicador),
  Nome = dplyr::pull(dados[2, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Polaridade = dplyr::pull(dados[4, ], indicador),
  Medida = dplyr::pull(dados[5, ], indicador),
  Valor = dplyr::pull(dados[6, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r vara`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'Parados100'

tabela <- dplyr::tibble(
  Limite = dplyr::pull(dados[1, ], indicador),
  Nome = dplyr::pull(dados[2, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Polaridade = dplyr::pull(dados[4, ], indicador),
  Medida = dplyr::pull(dados[5, ], indicador),
  Valor = dplyr::pull(dados[6, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
## {background-image="imagens/1.TJRR.png" background-opacity=".2"}
### `r vara`
::: {.columns}
::: {.column width="100%"}
```{r}
indicador <- 'IAD'

tabela <- dplyr::tibble(
  Limite = dplyr::pull(dados[1, ], indicador),
  Nome = dplyr::pull(dados[2, ], indicador),
  Descrição = dplyr::pull(dados[3, ], indicador),
  Polaridade = dplyr::pull(dados[4, ], indicador),
  Medida = dplyr::pull(dados[5, ], indicador),
  Valor = dplyr::pull(dados[6, ], indicador)
)

criar.tabela(tabela)
```
:::
:::
